Evapotranspiration mapping with Landsat 5TM in GRASS GIS

### 2011-01-04 tutorials/grass_landsat_ETa/article_GIPE.tex
Added Energy Balance Intro
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44848 15284696-431f-4ddb-bdfa-cd5b030d7da7

\section{Energy balance terms}
\subsection{Net Radiation}
Net radiation at satellite overpass (instantaneous) and integrated over the day are computed from a generic GRASS GIS raster module "r.sun". 
The r.sun program works in two modes. In the first mode it calculates for the image acquisition local time a solar incidence angle [degrees] and solar irradiance values [W.m-2]. In the second mode daily sums of solar radiation [Wh.m-2.day-1] are computed within a day.\newline

>>>>

\section{Energy balance terms}
The energy-balance models use visible, infrared and thermal remotely sensed data for solving the main equation:\newline
\begin{center}
Rn-G-H-$\lambda$ET=0 \newline
\end{center}
Where the Rn is the net radiation, H is the sensible heat flux, G is the soil heat flux, and $\lambda$ET is the latent heat flux.\newline
\subsection{Net Radiation}
Net radiation at satellite overpass (instantaneous) and integrated over the day are computed from a generic GRASS GIS raster module "r.sun". 
The r.sun program works in two modes. In the first mode it calculates for the image acquisition local time a solar incidence angle [degrees] and solar irradiance values [W.m-2]. In the second mode daily sums of solar radiation [Wh.m-2.day-1] are computed within a day.\newline
